A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Use "dat" rather than "data"
Because "data()" is already a function

# Load penguins data set
data <- read.csv("Data.csv")

# Remove rows with NA
data_clean <- data[complete.cases(data),]

# Perform t-test
t_test_result <- t.test(bill_length_mm ~ sex, data = data_clean)

@@

modelsummary::datasummary_balance(formula = ~ sex, data = data_clean, dinm = FALSE)

@@

blm_female <- data_clean$bill_length_mm[data_clean$sex == "female"]
blm_male <- data_clean$bill_length_mm[data_clean$sex == "male"]
```

@@

# Create ggplot object
ggplot2::ggplot(data_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    show.legend = FALSE
  ) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```

>>>>

# Load penguins data set
dat <- read.csv("Data.csv")

# Remove rows with NA
dat_clean <- dat[complete.cases(dat),]

# Perform t-test
t_test_result <- t.test(bill_length_mm ~ sex, data = dat_clean)

@@

modelsummary::datasummary_balance(formula = ~ sex, data = dat_clean, dinm = FALSE)

@@

blm_female <- dat_clean$bill_length_mm[dat_clean$sex == "female"]
blm_male <- dat_clean$bill_length_mm[dat_clean$sex == "male"]
```

@@

# Create ggplot object
ggplot2::ggplot(dat_clean, ggplot2::aes(x = sex, y = bill_length_mm, fill = sex), group = sex) +
  ggplot2::geom_violin(
    draw_quantiles = c(0.25, 0.5, 0.75),
    show.legend = FALSE
  ) +
  ggplot2::geom_jitter(width = 0.15, show.legend = FALSE) +
  ggplot2::labs(x = "Sex", y = "Bill length in mm") +
  ggplot2::theme_minimal()
```
